---
title: "txt to csv"
author: "Tyler Brown"
date: '`r Sys.Date()`'
output: html_document
---
## Project 1
In this project, you’re given a text file with chess tournament results where the information has some structure. Your
job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database)
with the following information for all of the players:
Player’s Name, Player’s State, Total Number of Points, Player’s Pre-Rating, and Average Pre Chess Rating of Opponents

## Loading the Data
Load the data from raw data in GitHub repository, which is available at <https://raw.githubusercontent.com/AlphaCurse/TXT_to_CSV/main/chesstornament.txt>.
```{r}
library(stringr)
library(readr)

url = 'https://raw.githubusercontent.com/AlphaCurse/TXT_to_CSV/main/chesstornament.txt'
df = readLines(url)
```

Visualize the data we have.
```{r}
head(df)
```

## Edit the Data
Seeing as the data is difficult to interpret, it'll need to be configured.
```{r}
#locate proper data
x0 = 0
x1 = unname(str_locate_all(pattern = '\\|', df[5])[[1]][1,1])
x2 = unname(str_locate_all(pattern = '\\|', df[5])[[1]][2,1])
x3 = unname(str_locate_all(pattern = '\\|', df[5])[[1]][3,1])
x4 = max(nchar(df))

#sequence and group
seq1 = seq(5, 196, 3)
seq2 = seq(6, 196, 3)
group1 = df[seq1]
group2 = df[seq2]
```

## Capture the Data
Now that the data is in a more organized format, we can begin capturing features.
```{r}
#group player names
name = substr(group1, x1 + 1, x2 - 2)
PlayerName = str_trim(name)

#group player state
state = substr(group2, x0, x1 - 1)
State = str_trim(state)

#group total points
totalpts = substr(group1, x2 + 1, x3 - 1)

#group pre-ratings
pre = substr(group2, x1 + 1, x2 - 1)
pre = str_extract(pre, ': *\\d{2,}')

#add each feature into dataframe
chess_df = data.frame(PlayerName, State)
chess_df$TotalPts = sprintf("%.1f", as.numeric(totalpts))
chess_df$PreRating = as.integer(str_extract(pre, '\\d{2,}'))
```


## Calculate Average Pre Rating of Opponent
To calculate the average pre rating of opponents, I used the following function...
```{r}
opp = substr(group1, x3 + 1, x4)
opp = str_extract_all(opp, '\\b\\d{1,}')
opp = as.matrix(opp)

avgoppprerate = function(y, z){
  x = y[z]
  
  for (a in x) {
    rate = 0
    c = 0
    for (b in a) {
      c = c + 1
      rate = rate + chess_df$PreRating[as.numeric(b)]
    }
    rate = round(rate/c)
  }
  return(rate)
}

chess_df$AvgOppPreRating = apply(opp, 1, avgoppprerate)
```

## Visualize DataFrame
```{r}
View(chess_df)
```

## Export txt file into csv file
```{r}
write.csv(chess_df, "tournamentinfo.csv")
```

## View CSV version
```{r}
csv_df = read_csv('https://raw.githubusercontent.com/AlphaCurse/TXT_to_CSV/main/tournamentinfo.csv')
csv_df
```

